Consumer Reviews and Product Discounts:\\ Evidence From Video Games

### 2020-08-12 Analysis/Code/Paper.Rmd
Merged the NLLS results with LS.

## Estimation and Results

@@

@@

@@

# Additional Tables and Figures
## Discounts Around Transitions
```{r results = 'asis'}
cat(star_insert_row(star.out.transitions, c("Time Effects & Weekdays, Week \\\\",
                                "Game Effects & $\\times$ \\\\",
                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(34,34,34)))
```
\newpage
## Review Lag
Table \ref{reviewLag} presents the results of estimating
$$NewReviews_{it} =\sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
+ reviewBin_{it} + age_{it} + young_{it} +  f_i + \tau_t + u_{it}$$
```{r include=F}
# Calculate the daily new review count and the lags of the dummy for new discount. 
panel[, new.reviews := c(reviews[1], diff(reviews)), by = ID]
panel[, discNewLag2 := shift(discNewLag), by = ID][is.na(discNewLag2), discNewLag2 := F]
panel[, discNewLag3 := shift(discNewLag2), by = ID][is.na(discNewLag3), discNewLag3 := F]
panel[, discNewLag4 := shift(discNewLag3), by = ID][is.na(discNewLag4), discNewLag4 := F]
panel[, discNewLag5 := shift(discNewLag4), by = ID][is.na(discNewLag5), discNewLag5 := F]
panel[, discNewLag6 := shift(discNewLag5), by = ID][is.na(discNewLag6), discNewLag6 := F]
panel[, discNewLag7 := shift(discNewLag6), by = ID][is.na(discNewLag7), discNewLag7 := F]

@@

>>>>

## Results

In this section I present the estimates of the model parameters. I start with the demand parameters $(\lambda_i, \psi_i, \beta)$ in (\ref{arrivalReg}), and contrast these estimates with the ones delivered by running a regression (\ref{logReg}). Then I proceed to the parameters of the review process, where the focus will be on the contributions $(\rho_{1i}^+, \rho_{1i}^-)$ of discounts to the like and dislike rates.

@@

An ideal set of covariates $x_{it}$ that I would like to use in estimating (\ref{arrivalReg}), given by
$$
A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
$$
\noindent would be price, the review label, log reviews, age (plus a dummy for being at most 14 days old), and a set of day of the week and sample week time effects. However, this proved to be computationally infeasible. Even though I manage to concentrate out $2n=$`r 2*info[, .N]` game-specific parameters $(\lambda_i, \psi_i)$ from the numerical optimization routine, estimation of $\beta$ still relies on minimizing the sum of squared residuals in a $\dim(\beta)$-dimensional space. The routine would fail to converge to a solution within reasonable boundaries, so I had to eliminate some regressors.

@@

```{r results='asis'}
reg1 <- plm(log(number) ~ log(numberLag) + log(price) + noScore +
              negative + mPositive + positive + log(reviews+1) + 
              age + young + discSeason + day,
                 data=panel[price!=0,],
            model="within")

reg2 <- plm(log(number) ~ log(numberLag) + log(price) + noScore + 
              negative + mPositive + realPositive + vPositive + 
              ovPositive + log(reviews+1) + age + young + 
              day + week,
                data=panel[price!=0,],
            model="within")

res <- plmJuliaToTex(reg1, reg2, reg.results[, c(1,4)],
                     reg.results.stats[, c(1,4)])
rm(reg.results, reg.results.stats)

table <- texreg(res,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("NLLS", "Reg", "Full Reg"),
                reorder.coef = c(1, 9, 2, 3, 8, 10, 
                                 4, 5, 6, 7, 11, 12),
                caption = "Estimates of the Demand Parameters",
                caption.above = T,
                label = "demandEstimates")

season.location <- str_locate(table, c("Weekdays"))[1]
table.bottom <- str_sub(table, season.location, str_length(table))
table.top <- str_sub(table, 1, season.location - 1)
table.bottom <- str_replace_all(table.bottom, "0.000", "\\\\times")
table.bottom <- str_replace_all(table.bottom, "1.000", "\\\\checkmark")
table.bottom <- str_replace_all(table.bottom, ".000", "")
table <- paste(table.top, table.bottom, sep = "")
class(table) <- c("character", "texregTable")
table
```

The week effects contribute the most to the dimensionality of the problem, as there are `r panel[, length(unique(week))]` weeks in the sample. The reason to include these week effects is to account for platform-wide shocks. The biggest shocks shared by games on Steam are Seasonal Sales. These sales take place around major holidays, and, thus, blend together the increased platform-wide demand with the higher quantity demanded caused by the plethora of price promotions (depicted in Figure \ref{seasonalSales}). To capture these periods in a parsimonious way, I calculated the average daily discount in the sample, and labeled the days when the average discount exceeded 20\%. Figure \ref{seasonalSalesPeriods} in the Appendix shows that my definition tracks closely the spikes in the aggregate discounting behavior. I also tried using the raw value of the average discount in the sample, but the results remained the same.

Another exclusion I have to make is that of the “Very Positive” and “Overwhelmingly Positive” review lables. While the latter is not very prevalent in the sample, as is depicted in Figure \ref{reviewDescriptivePlots}, the former is by far the most common review label. In order to avoid dropping out these observations, I pool the “Very Positive” and “Overwhelmingly Positive” labels together with the “Positive” label. Recall that the only difference between “Positive” and “Very Positive” is whether the game has less or more than 50 reviews, so this pooling averages between two similar and adjacent review labels.

Thus, the final set of covariates that I use in estimating (\ref{arrivalReg}) are: price, review label, log reviews, two age variables, and a set of day of the week time effects, and a Seasonal Sale dummy. I mentioned in the Identification section that a more simplistic, yet more tractable, alternative to estimating the non-linear model (\ref{arrivalReg}) is given by equation (\ref{logReg})
$$
\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
$$
\noindent To check whether the omitted covariates could be playing a crucial role, I will report the results of estimaing (\ref{logReg}) both with the ideal set of covariates, and with the covariates used to estimate (\ref{arrivalReg}). The results are presented in Table \ref{demandEstimates}.

@@

# Additional Tables and Figures
## Discounts Around Transitions

```{r results = 'asis'}
cat(star_insert_row(star.out.transitions, c("Time Effects & Weekdays, Week \\\\",
                                "Game Effects & $\\times$ \\\\",
                                "Polynomial($t$ W/O Discount) & $d = 2$ \\\\"), insert.after = c(34,34,34)))
```

\newpage
## Review Lag
Table \ref{reviewLag} presents the results of estimating
$$NewReviews_{it} =\sum_{l = 0}^{7} \mathds{1}(\text{Disc. } l \text{ days ago})
+ reviewBin_{it} + age_{it} + young_{it} +  f_i + \tau_t + u_{it}$$
```{r include=F}
# Calculate the daily new review count and the lags of the dummy for new discount. 
panel[, new.reviews := c(reviews[1], diff(reviews)), by = ID]
panel[, discNewLag2 := shift(discNewLag), by = ID][is.na(discNewLag2), discNewLag2 := F]
panel[, discNewLag3 := shift(discNewLag2), by = ID][is.na(discNewLag3), discNewLag3 := F]
panel[, discNewLag4 := shift(discNewLag3), by = ID][is.na(discNewLag4), discNewLag4 := F]
panel[, discNewLag5 := shift(discNewLag4), by = ID][is.na(discNewLag5), discNewLag5 := F]
panel[, discNewLag6 := shift(discNewLag5), by = ID][is.na(discNewLag6), discNewLag6 := F]
panel[, discNewLag7 := shift(discNewLag6), by = ID][is.na(discNewLag7), discNewLag7 := F]

@@

\newpage
## Definition of Seasonal Sales
```{r seasonal-sales-periods, fig.cap='\\label{seasonalSalesPeriods} Seasonal Sales and Discounting Activity. Shaded regions are my definition of Seasonal Sales periods. The first spike on the graph is excluded because the sample starts with just one game, and I exclude the first 2 weeks from the calculations.'}
months1 <- c(-1, 30, 58, 89, 119, 150, 180, 211, 242, 272, 303, 333) + 1
months2 <- c(333 + 32 + months1, 699 + 31)

f<-panel[, .(disc = discSeason[1]), keyby = t][, .(t, z=c(NA, diff(disc)))]

discPeriods <- data.frame(xstart = f[z==1, t], xend = c(f[z==-1, t], panel[, max(t)]))

ggplot(data = panel[, .(y=sum(discount > 0)/(.N), z=avDisc[1]), by = t]) +
  geom_rect(data = discPeriods, aes(xmin = xstart, xmax = xend, ymin = -Inf, ymax = Inf), fill = my.colors[2], alpha = 0.25) + 
  # ggtitle() +
  geom_line(aes(x = t, y = y),
            color = my.colors[1],
            size = 1) +
  scale_x_continuous(name = NULL,
                     breaks = c(months1, months2)[seq(1,25,3)], 
                     labels = months(getDate(c(months1, months2))[seq(1,25,3)], 
                                     abbreviate=T),
                     minor_breaks = NULL) +
  scale_y_continuous(name = "Fraction of Games",
                     minor_breaks = NULL)  +
  my.theme(leg.x = 0.25, leg.y = 0.9)

rm(months1, months2, f, discPeriods)
```

### 2020-08-12 Analysis/Output/Paper.tex
Merged the NLLS results with LS.

\title{Consumer Reviews and Product Discounts:\\
Evidence From Video Games}
\author{Dmitry Sorokin}
\date{August 09, 2020}

@@

 \caption{\label{steamStore}Example Browsing Session on Steam}\label{fig:unnamed-chunk-3}
 \end{figure}

@@

\hypertarget{estimation-and-results}{%
\subsection{Estimation and Results}\label{estimation-and-results}}

@@

@@

\begin{table}[hp] \centering    \caption{Discounts In The Days Around Transition}    \label{transitionReg}  \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Discount Probability \\  \hline \\[-1.8ex]   Days to Transition & 0.006$^{***}$ \\    & (0.0005) \\    Days After Transition & $-$0.011$^{***}$ \\    & (0.0005) \\    No Score & 0.181$^{***}$ \\    & (0.026) \\    Negative & 0.004 \\    & (0.010) \\    Mostly Positive & $-$0.001 \\    & (0.005) \\    Positive & 0.032$^{***}$ \\    & (0.007) \\    Very Positive & 0.001 \\    & (0.006) \\    Ov. Positive & 0.004 \\    & (0.013) \\    Log Reviews & $-$0.011$^{***}$ \\    & (0.002) \\    Age & 0.0003$^{***}$ \\    & (0.00001) \\    Const & 0.872$^{***}$ \\    & (0.014) \\   \hline \\[-1.8ex]  Time Effects & Weekdays, Week \\ Game Effects & $\times$ \\ Polynomial($t$ W/O Discount) & $d = 2$ \\ Observations & 32,412 \\  R$^{2}$ & 0.397 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{table} 
\newpage

@@

>>>>

\title{Consumer Reviews and Product Discounts:\\
Evidence From Video Games}
\author{Dmitry Sorokin}
\date{August 12, 2020}

@@

 \caption{\label{steamStore}Example Browsing Session on Steam}\label{fig:unnamed-chunk-5}
 \end{figure}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

In this section I present the estimates of the model parameters. I start
with the demand parameters \((\lambda_i, \psi_i, \beta)\) in
(\ref{arrivalReg}), and contrast these estimates with the ones delivered
by running a regression (\ref{logReg}). Then I proceed to the parameters
of the review process, where the focus will be on the contributions
\((\rho_{1i}^+, \rho_{1i}^-)\) of discounts to the like and dislike
rates.

@@

An ideal set of covariates \(x_{it}\) that I would like to use in
estimating (\ref{arrivalReg}), given by \[
A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
\] \noindent would be price, the review label, log reviews, age (plus a
dummy for being at most 14 days old), and a set of day of the week and
sample week time effects. However, this proved to be computationally
infeasible. Even though I manage to concentrate out \$2n=\$1812
game-specific parameters \((\lambda_i, \psi_i)\) from the numerical
optimization routine, estimation of \(\beta\) still relies on minimizing
the sum of squared residuals in a \(\dim(\beta)\)-dimensional space. The
routine would fail to converge to a solution within reasonable
boundaries, so I had to eliminate some regressors.

\begin{table}
\caption{Estimates of the Demand Parameters}
\begin{center}
\begin{tabular}{l c c c}
\hline
 & NLLS & Reg & Full Reg \\
\hline
Log Price     & $-0.118^{***}$ & $-0.100^{***}$ & $-0.114^{***}$ \\
              & $(0.027)$      & $(0.004)$      & $(0.004)$      \\
Seasonal Sale & $-0.004$       & $0.063^{***}$  &                \\
              & $(0.012)$      & $(0.003)$      &                \\
Age           & $-0.137$       & $-0.000^{***}$ & $0.001^{***}$  \\
              & $(0.458)$      & $(0.000)$      & $(0.000)$      \\
Age $\le 14$  & $0.081^{**}$   & $0.147^{***}$  & $0.172^{***}$  \\
              & $(0.041)$      & $(0.006)$      & $(0.006)$      \\
Log Reviews   & $-0.120^{***}$ & $0.025^{***}$  & $0.024^{***}$  \\
              & $(0.006)$      & $(0.005)$      & $(0.006)$      \\
Lag Players   &                & $0.795^{***}$  & $0.790^{***}$  \\
              &                & $(0.002)$      & $(0.002)$      \\
No Score      & $0.565^{***}$  & $0.085^{***}$  & $0.090^{***}$  \\
              & $(0.098)$      & $(0.011)$      & $(0.011)$      \\
Negative      & $0.053$        & $-0.088^{***}$ & $-0.088^{***}$ \\
              & $(0.047)$      & $(0.017)$      & $(0.017)$      \\
M. Positive   & $0.064^{***}$  & $0.058^{***}$  & $0.066^{***}$  \\
              & $(0.023)$      & $(0.007)$      & $(0.007)$      \\
Positive      & $0.078^{**}$   & $0.099^{***}$  & $0.095^{***}$  \\
              & $(0.031)$      & $(0.009)$      & $(0.009)$      \\
V. Positive   &                &                & $0.118^{***}$  \\
              &                &                & $(0.009)$      \\
Ov. Positive  &                &                & $0.142^{***}$  \\
              &                &                & $(0.011)$      \\
\hline
Weekdays      & $\checkmark$        & $\checkmark$        & $\checkmark$        \\
Week          & $\times$        & $\times$        & $\checkmark$        \\
Observations  & $355983$   & $355586$   & $355669$   \\
R$^2$         & $0.930$        & $0.706$        & $0.707$        \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
\end{tabular}
\label{demandEstimates}
\end{center}
\end{table}

The week effects contribute the most to the dimensionality of the
problem, as there are 105 weeks in the sample. The reason to include
these week effects is to account for platform-wide shocks. The biggest
shocks shared by games on Steam are Seasonal Sales. These sales take
place around major holidays, and, thus, blend together the increased
platform-wide demand with the higher quantity demanded caused by the
plethora of price promotions (depicted in Figure \ref{seasonalSales}).
To capture these periods in a parsimonious way, I calculated the average
daily discount in the sample, and labeled the days when the average
discount exceeded 20\%. Figure \ref{seasonalSalesPeriods} in the
Appendix shows that my definition tracks closely the spikes in the
aggregate discounting behavior. I also tried using the raw value of the
average discount in the sample, but the results remained the same.

Another exclusion I have to make is that of the ``Very Positive'' and
``Overwhelmingly Positive'' review lables. While the latter is not very
prevalent in the sample, as is depicted in Figure
\ref{reviewDescriptivePlots}, the former is by far the most common
review label. In order to avoid dropping out these observations, I pool
the ``Very Positive'' and ``Overwhelmingly Positive'' labels together
with the ``Positive'' label. Recall that the only difference between
``Positive'' and ``Very Positive'' is whether the game has less or more
than 50 reviews, so this pooling averages between two similar and
adjacent review labels.

Thus, the final set of covariates that I use in estimating
(\ref{arrivalReg}) are: price, review label, log reviews, two age
variables, and a set of day of the week time effects, and a Seasonal
Sale dummy. I mentioned in the Identification section that a more
simplistic, yet more tractable, alternative to estimating the non-linear
model (\ref{arrivalReg}) is given by equation (\ref{logReg}) \[
\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}
\] \noindent To check whether the omitted covariates could be playing a
crucial role, I will report the results of estimaing (\ref{logReg}) both
with the ideal set of covariates, and with the covariates used to
estimate (\ref{arrivalReg}). The results are presented in Table
\ref{demandEstimates}.

@@

\begin{table}[hp] \centering    \caption{Discounts In The Days Around Transition}    \label{transitionReg}  \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Discount Probability \\  \hline \\[-1.8ex]   Days to Transition & 0.006$^{***}$ \\    & (0.0005) \\    Days After Transition & $-$0.011$^{***}$ \\    & (0.0005) \\    No Score & 0.181$^{***}$ \\    & (0.026) \\    Negative & 0.004 \\    & (0.010) \\    Mostly Positive & $-$0.001 \\    & (0.005) \\    Positive & 0.032$^{***}$ \\    & (0.007) \\    Very Positive & 0.001 \\    & (0.006) \\    Ov. Positive & 0.004 \\    & (0.013) \\    Log Reviews & $-$0.011$^{***}$ \\    & (0.002) \\    Age & 0.0003$^{***}$ \\    & (0.00001) \\    Const & 0.872$^{***}$ \\    & (0.014) \\   \hline \\[-1.8ex]  Time Effects & Weekdays, Week \\ Game Effects & $\times$ \\ Polynomial($t$ W/O Discount) & $d = 2$ \\ Observations & 32,412 \\  R$^{2}$ & 0.397 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  \end{table}

@@

\hypertarget{definition-of-seasonal-sales}{%
\subsection{Definition of Seasonal
Sales}\label{definition-of-seasonal-sales}}

{\centering \includegraphics{/Users/Dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/seasonal-sales-periods-1}

\caption{\label{seasonalSalesPeriods} Seasonal Sales and Discounting Activity. Shaded regions are my definition of Seasonal Sales periods. The first spike on the graph is excluded because the sample starts with just one game, and I exclude the first 2 weeks from the calculations.}\label{fig:seasonal-sales-periods}
\end{figure}
